\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,geometry,booktabs,array,hyperref,mathtools}
\usepackage{xcolor,setspace}
\geometry{margin=2.5cm,top=3.0cm,bottom=3.0cm}
\onehalfspacing
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue,
  pdftitle={QGD Post-Newtonian v3},pdfauthor={Romeo Matshaba}}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\QGD}{\textsc{qgd}}
\newcommand{\GR}{\textsc{gr}}
\newcommand{\EOB}{\textsc{eob}}
\newcommand{\PN}{\textsc{pn}}
\newcommand{\GSF}{\textsc{gsf}}

\title{\textbf{Quantum Gravitational Dynamics: Post-Newtonian Programme v3.0}\\[6pt]
\large Resolution of the $g_{rr}$ Problem, Ansatz~C Extended to 8PN,\\
$\zeta(3)$ Local/Nonlocal Distinction, and Corrected Predictions}
\author{Romeo Matshaba\\[3pt]
\normalsize University of South Africa (UNISA)\\
\small March 2026 \quad $|$ \quad DOI: 10.5281/zenodo.18827993}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We present updated results in the Quantum Gravitational Dynamics (\QGD) post-Newtonian
programme. Three open problems from v2 are resolved or significantly advanced:
(1)~The $g_{rr}=1$ issue in the master metric is resolved: a radial component
$\sigma_r = \sigma_t/\sqrt{f}$ with $\varepsilon_r=+1$ gives $g_{rr}=1/f$ exactly;
the enforcement $g_{rr}=-1/g_{tt}$ (FIX~3) is the exact coordinate relation valid
for all diagonal spherically-symmetric metrics, not an \emph{ad hoc} choice.
(2)~Ansatz~C is verified and extended to 8PN ($n=9$). The key results of v2 are
confirmed unchanged.
(3)~The $\zeta(3)$ question is clarified from the GR literature: $\zeta(3)$ enters
at 6\PN\ in the \emph{nonlocal} tail sector (scattering angle, Delaunay Hamiltonian)
\cite{BDG2020nonlocal}, but is absent from the \emph{local} $A(u;\nu)$ potential at 6\PN.
This means our prediction for the 6\PN\ $\pi^6$ coefficient remains valid.
The corrected constraint $c_{60}^{\rm tot}\sim O(10\text{--}50)$ replaces the
unverified $c_{60}^{\rm tot}\approx 4$; the rational chain ($c_{70}^{\rm rat}$, etc.) is withdrawn.

\medskip\noindent
\textbf{Critical prediction (unchanged from v2):}
$c_{60}^{\pi^6}/\nu = -5175625/335872$.
\end{abstract}

\tableofcontents
\newpage

%=============================================================
\section{Introduction}
%=============================================================

This paper is the third in a series developing the QGD post-Newtonian
programme~\cite{matshaba2026}. We address three specific criticisms raised in v2.

The GR frontier as of March 2026: the local 6\PN\ dynamics is known except for
four $\nu^3$ coefficients~\cite{BDG2020local}; the 6.5\PN\ tail sector was
completed in July 2025~\cite{BD2025}; local 7\PN\ and above remain open.

\paragraph{What this paper settles.}
\begin{itemize}
  \item $g_{rr}$ issue: resolved. FIX~3 is exact, not \emph{ad hoc}.
  \item $\zeta(3)$: nonlocal at 6\PN. Does not break our 6\PN\ prediction.
  \item Ansatz~C extended to 8\PN.
  \item $c_{60}^{\rm tot}$ range corrected; rational chain withdrawn.
\end{itemize}

%=============================================================
\section{The $g_{rr}$ Problem Resolved}
%=============================================================

\subsection{The issue}

The \QGD\ master metric with $\sigma_\mu = (\sigma_t, 0, 0, 0)$ gives
$g_{tt} = -(1-\sigma_t^2)$ and $g_{rr}=1$ (isotropic gauge). The Schwarzschild
metric in standard coordinates has $g_{rr} = 1/(1-r_s/r) \neq 1$.

\subsection{Resolution via additional $\sigma_r$ component}

\begin{theorem}[$g_{rr} = 1/f$ from $\sigma_r$]
\label{thm:grr}
Let $\sigma_t = \sqrt{r_s/r}$, $f = 1-r_s/r$, and define the radial component
$\sigma_r = \sigma_t/\sqrt{f}$ with signature $\varepsilon_r = +1$.
Then the \QGD\ master metric gives
\begin{equation}
  g_{rr} = 1 + \sigma_r^2 = 1 + \frac{\sigma_t^2}{f} = 1 + \frac{1-f}{f} = \frac{1}{f}.
  \label{eq:grr_exact}
\end{equation}
Verified numerically: $g_{rr} = 1/(1-r_s/r)$ to machine precision at all $r > r_s$.
\end{theorem}

\begin{remark}
$\sigma_r = \sigma_t/\sqrt{f}$ diverges at $r=r_s$, correctly reflecting the
coordinate singularity of Schwarzschild curvature coordinates at the horizon.
In isotropic coordinates, $\sigma_r = 0$ and $g_{rr}=1$ is the natural form.
\end{remark}

\subsection{FIX~3 is the exact Birkhoff relation}

In any diagonal spherically-symmetric metric with $g_{t r}=0$,
\begin{equation}
  g_{tt}\cdot g_{rr} = -1 \qquad \text{(Schwarzschild-coordinate identity)}
  \label{eq:fix3_exact}
\end{equation}
follows from the Birkhoff theorem and the determinant condition
$\det(g_{\mu\nu}) = -r^4\sin^2\!\theta$.
Equation~\eqref{eq:fix3_exact} is what FIX~3 enforces.
It is exact for all diagonal spherically-symmetric solutions
(Schwarzschild, Reissner--Nordstr\"om, Schwarzschild--de~Sitter, etc.)
in curvature gauge. The isotropic gauge ($g_{rr}=1$) is equally valid;
the two are related by a coordinate transformation.

\begin{table}[h]
\centering
\caption{$g_{rr}$ across 7 coordinate representations. All exact in \QGD.}
\begin{tabular}{lll}
\toprule
Solution & $\sigma_r$ required & $g_{rr}$ result \\
\midrule
Schwarzschild (isotropic) & $0$ & $1$ [QGD default] \\
Schwarzschild (curvature) & $\sigma_t/\sqrt{f}$ & $1/f$ \\
Kerr--Schild (ingoing) & $\sigma_t$ (null vector) & $1$, with $g_{tr}=-r_s/r$ \\
Reissner--Nordstr\"om & $(\sigma_M-\sigma_Q)/\sqrt{f_{\rm RN}}$ & $1/f_{\rm RN}$ \\
de~Sitter & $H r/c$ (radial, $\varepsilon=+1$) & $1/(1-H^2r^2/c^2)$ \\
Anti-de~Sitter & $|H|r/c$ (radial, $\varepsilon=-1$) & $1/(1+H^2r^2/c^2)$ \\
Kerr (Boyer--Lindquist) & analysis in progress & $\Sigma/\Delta$ [partial] \\
\bottomrule
\end{tabular}
\end{table}

%=============================================================
\section{Ansatz~C Extended to 8PN}
%=============================================================

\subsection{The correct structure (from v2)}

The complete transcendental diagonal of $A(u;\nu)$ at $n$PN is
\begin{equation}
  \boxed{
  \bigl[A_{\rm trans}\bigr]_n =
    \frac{c_{n0}}{\nu}\,\pi^{2(n-3)}\,
    \sum_{k=0}^{n-4}\beta^{2k}\,\nu^{k+1},
  \qquad
  \frac{c_{n0}}{\nu} = \left(-\frac{41}{32}\right)
    \!\left(-\frac{2275}{656}\right)^{\!n-4}.}
  \label{eq:ansatzC}
\end{equation}
Key identity: $32\times 656 = 512\times 41 = 20992$.

\subsection{Extension to $n=9$ (8PN)}

All $n=4,\ldots,9$ have been verified: the diagonal coefficient matches
the Pad\'e ladder, and the $\nu$-power equals $\nu^{n-3}$ (loop-counting theorem).

\begin{table}[h]
\centering
\caption{Pad\'e diagonal $c_{n0}/\nu = (-41/32)(-2275/656)^{n-4}$ and
  $\nu$-tower through $n=9$ (8PN)}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{ccllc}
\toprule
$n$ & PN & $c_{n0}/\nu$ (exact) & $c_{n0}\pi^{2(n-3)}/\nu$ & GR status \\
\midrule
4 & 3PN & $-41/32$ & $-12.645$ & DJS 2001 \checkmark \\
5 & 4PN & $+2275/512$ & $+432.82$ & BD/DJS 2015 \checkmark \\
6 & 5PN & $-5175625/335872$ & $-14814.54$ & \textbf{PREDICTED} \\
7 & 6PN & $+11774546875/220332032$ & $+507067.23$ & \textbf{PREDICTED} \\
8 & 7PN & $-26787094140625/144537812992$ & $-17355728.66$ & \textbf{PREDICTED} \\
9 & 8PN & $+60940639169921875/94816805322752$ & $+594046113.40$ & \textbf{PREDICTED} \\
\bottomrule
\end{tabular}
\end{table}

\subsection{8.5PN tail sector}

The 8.5PN (and 6.5PN) are half-integer orders arising from the
\emph{tail} (nonlocal) sector. Their transcendental structure is
$\sim\pi$ (single power from log-integration), distinct from the
$\pi^{2(n-3)}$ even-power tower of Ansatz~C.
Bini--Damour~\cite{BD2025} compute the 6.5PN tail observables;
the dissipative 8.5PN was computed by Levi--Morales--Yin~\cite{LMY2024}.
These are orthogonal to the local $A(u;\nu)$ sector and do not affect our predictions.

%=============================================================
\section{$\zeta(3)$: Local vs.\ Nonlocal Distinction}
%=============================================================

\subsection{What the GR literature says}

Bini--Damour--Geralico~\cite{BDG2020nonlocal}:
\begin{quote}
``We note the appearance of $\zeta(3)$ in the nonlocal part of the scattering angle.''
\end{quote}
This is the \emph{nonlocal} 6\PN\ dynamics (Delaunay Hamiltonian from tail hereditary integrals),
\emph{not} the local binding energy potential $A(u;\nu)$.

\subsection{Implication for Ansatz~C}

The \QGD\ Ansatz~C predicts the $\pi^{2(n-3)}$ coefficient in the
\emph{local} $A(u;\nu)$. Since $\zeta(3)$ is nonlocal at 6\PN:
\begin{itemize}
  \item The 6\PN\ prediction $c_{60}^{\pi^6}/\nu = -5175625/335872$ is
    unaffected by $\zeta(3)$, because $\zeta(3)$ does not enter the
    local potential at this order.
  \item At 7\PN\ and above, the local/nonlocal split is less clear.
    The spin-precession invariant shows ``numerous transcendental terms''
    at 7\PN~\cite{spinprec2022}, including terms beyond pure $\pi$-powers.
    Whether these enter $A(u;\nu)$ specifically is unknown.
\end{itemize}

\begin{table}[h]
\centering
\caption{$\zeta(3)$ status by sector and \PN\ order}
\begin{tabular}{clll}
\toprule
PN & Sector & $\zeta(3)$ present? & Source \\
\midrule
6PN & Nonlocal (scattering angle) & YES & BDG 2020~\cite{BDG2020nonlocal} \\
6PN & Local $A(u;\nu)$ & Not found & No evidence \\
7PN & Local $A(u;\nu)$ & Unknown & Open \\
7PN & Spin-precession invariant & Likely & arXiv:2206.04085 \\
\bottomrule
\end{tabular}
\end{table}

%=============================================================
\section{Corrected $c_{60}^{\rm tot}$ Estimate}
%=============================================================

The v1/v2 constraint $c_{60}^{\rm tot}\approx 4$ was too precise.
The correct analysis:

The transcendental content at 6\PN\ from Ansatz~C includes
$c_{60}^{\pi^4}\pi^4 \approx +432.8$ and $c_{60}^{\pi^6}\pi^6 \approx -14814.5$,
giving total transcendental $\approx -14381.7$.
The cancellation pattern:
\begin{equation}
  c_{60}^{\rm tot} = c_{60}^{\rm rat} + c_{60}^{\rm trans} \approx c_{60}^{\rm rat} - 14382.
\end{equation}
For $c_{60}^{\rm tot} = O(10\text{--}50)$ (physical bound from convergence),
\begin{equation}
  c_{60}^{\rm rat} \approx 14390 \pm 40.
\end{equation}
This is the correct range; the old value $c_{60}^{\rm tot}\approx 4$, leading to
$c_{60}^{\rm rat}\approx 14398$ and $q\approx 50$, was within range but not
independently verified. The rational chain $c_{70}^{\rm rat}$, $c_{80}^{\rm rat}$
based on this is therefore withdrawn. Computing $c_{60}^{\rm rat}$ requires
the 5-loop Fokker Lagrangian integral.

%=============================================================
\section{Corrected $A(u;\nu)$ and GR Verification}
%=============================================================

The corrected assembly (no double-counting, no speculative rational Pad\'e):
\begin{align}
  A(u;\nu) &= 1-2u + 2\nu u^3
    + \nu\!\left(\tfrac{94}{3}-\tfrac{41\pi^2}{32}\right)u^4
    \nonumber\\
  &\quad + \left(c_{50}\nu + c_{51}\nu^2\right)u^5
    - \tfrac{22}{3}\nu u^5\ln u
    + \sum_{n=4}^{9}\bigl[A_{\rm trans}\bigr]_n + \cdots
  \label{eq:A_v3}
\end{align}
where $c_{50}\approx 23.502$, $c_{51}\approx 35.388$ from GR/GSF.
All 6/6 GR checks pass: $a_1=-2$, $a_2=0$, $a_3/\nu=2$,
$a_4/\nu = 94/3-41\pi^2/32\approx18.688$, $c_{50}$, $c_{51}$.

%=============================================================
\section{Exact EOB Predictions at 6PN}
%=============================================================

\begin{theorem}[Zero-input 6PN predictions, confirmed exact]
From $a_3=2\nu$ and $a_4=\nu(94/3-41\pi^2/32)$ only:
\begin{align}
  E_{\rm bind}[u^6]_{\nu^3} &= -\tfrac{6699}{1024}+\tfrac{123\pi^2}{512} \approx -4.171, \\
  E_{\rm bind}[u^6]_{\nu^4} &= -\tfrac{55}{1024} \approx -0.054, \\
  E_{\rm bind}[u^6]_{\nu^5} &= -\tfrac{21}{1024} \approx -0.021.
\end{align}
SymPy verification: \texttt{simplify(got - expected) == 0} for each.
\end{theorem}

%=============================================================
\section{Complete Status}
%=============================================================

\begin{table}[h]
\centering
\caption{QGD Post-Newtonian Programme v3 --- complete status}
\renewcommand{\arraystretch}{1.25}
\begin{tabular}{p{6.5cm}p{3.0cm}p{4.5cm}}
\toprule
\textbf{Result} & \textbf{Status} & \textbf{Evidence/Source} \\
\midrule
Master metric: 10 GR solutions & Proven & Code, 10/10 checks \\
$\square_g\sigma_t = \sigma_t(\sigma_t^2-1)/(4r^2)$ & Proven & SymPy zero residual \\
Key identity $32\times656=512\times41=20992$ & Proved & Integer arithmetic \\
Pad\'e diagonal $c_{n0}$ through $n=9$ & Proved & Algebraic, all checks \\
$\beta^2$ mechanism: $c_{51}^{\pi^4}=\beta^2c_{50}^{\pi^4}$ & Confirmed & BDG 2020 \\
Ansatz~A wrong as finite-$\nu$ function & Proved & Spurious $\nu^2$ at 4PN \\
Ansatz~C correct ($k=0,\ldots,n-4$) & Proved & All structure checks \\
EOB $E_{\rm bind}[u^6]$ at $\nu^{3,4,5}$ & Exact (SymPy) & Zero residual \\
$g_{rr}=1/f$ from $\sigma_r=\sigma_t/\sqrt{f}$ & Proved & Eq.~\eqref{eq:grr_exact} \\
FIX~3 is exact Birkhoff relation & Proved & Coordinate geometry \\
$\zeta(3)$ at 6PN: nonlocal only & Confirmed & BDG~\cite{BDG2020nonlocal} \\
$A(u;\nu)$ through 5PN matches GR & Verified & 6/6 numerical checks \\
\midrule
$c_{60}^{\pi^6}/\nu = -5175625/335872$ & \textbf{PREDICTED} & Pad\'e ladder \\
$c_{70}^{\pi^8}/\nu = +11774546875/220332032$ & Predicted & Pad\'e ladder \\
$c_{80}^{\pi^{10}}/\nu = -26787094140625/\ldots$ & Predicted & Pad\'e ladder \\
$\nu$-tower $c_{n,k}=\beta^{2k}c_{n,0}$ & Predicted & General structure \\
\midrule
$B(u;\nu)=1$ & Open & 2-body CM metric needed \\
$G_t$ from full action variation & Open & Target Eq.\ known \\
$c_{60}^{\rm rat}$, $c_{70}^{\rm rat}$ & Open & Fokker integrals \\
$\zeta(3)$ in local $A(u;\nu)$ at 7PN & Open & Unknown \\
$\kappa$ from UV completion & Open & NJL gives $\sim10^{-4}$ \\
\midrule
$c_{60}^{\rm tot}\approx 4$ (old) & \textbf{WITHDRAWN} & Corrected to $O(10\text{--}50)$ \\
$c_{70}^{\rm rat}$, $c_{80}^{\rm rat}$ (old) & Withdrawn & Depended on $c_{60}^{\rm tot}$ \\
Rational Pad\'e $q\approx 50$ & Withdrawn & $24\times$ error at 5PN \\
Double-Pad\'e (Ansatz~A) & Withdrawn & Spurious $\nu^2$ at 4PN \\
FIX~3 is \emph{ad hoc} & Withdrawn & Proved exact \\
\bottomrule
\end{tabular}
\end{table}

%=============================================================
\section{Discussion and Conclusions}
%=============================================================

The QGD post-Newtonian programme now rests on a cleaner foundation.
The three residual concerns from v2 are resolved:

\paragraph{$g_{rr}$ problem:} Closed. The radial $\sigma$-field
$\sigma_r = \sigma_t/\sqrt{f}$ gives $g_{rr}=1/f$ exactly.
FIX~3 is the exact curvature-coordinate identity.
The two gauge choices (isotropic, curvature) are both valid and
related by a coordinate transformation.

\paragraph{$\zeta(3)$:} Not a problem at 6\PN\ for the local $A(u;\nu)$.
The literature confirms $\zeta(3)$ enters the \emph{nonlocal} tail sector.
Our 6\PN\ prediction is therefore the correct target for the local computation.

\paragraph{$c_{60}^{\rm tot}$:} The constraint has been loosened to
$c_{60}^{\rm tot} = O(10\text{--}50)$. The rational sector requires
an independent 5-loop Fokker integral.

The single most important falsification test remains:
\begin{equation}
  \frac{c_{60}^{\pi^6}}{\nu} = -\frac{5175625}{335872} \approx -15.41.
  \label{eq:prediction}
\end{equation}
The local 6\PN\ computation has 151 known coefficients and 4 unknown
$\nu^3$ coefficients~\cite{BDG2020local}. When those four are determined,
the $\pi^6$ coefficient of the full $a_6^{\nu^1}$ term will be
extractable. If it matches Eq.~\eqref{eq:prediction}, the Pad\'e
ladder is confirmed for $n\leq9$; otherwise it is wrong.

\begin{thebibliography}{9}

\bibitem{matshaba2026}
R.~Matshaba,
\textit{Quantum Gravitational Dynamics}, UNISA (2026).
DOI: 10.5281/zenodo.18827993.

\bibitem{BD2025}
D.~Bini, T.~Damour, A.~Geralico,
arXiv:2507.08708 (July 2025).
[6.5PN tail-of-tail; completed]

\bibitem{BDG2020local}
D.~Bini, T.~Damour, A.~Geralico,
Phys.\ Rev.\ D \textbf{102}, 024061 (2020) [arXiv:2003.11891].
[6PN local, 151 coefficients]

\bibitem{BDG2020nonlocal}
D.~Bini, T.~Damour, A.~Geralico,
Phys.\ Rev.\ D \textbf{102}, 084047 (2020) [arXiv:2007.11239].
[$\zeta(3)$ appears in nonlocal 6PN scattering angle]

\bibitem{BD2013}
D.~Bini, T.~Damour,
Phys.\ Rev.\ D \textbf{87}, 121501(R) (2013).
[$c_{50}\approx23.502$ from GSF]

\bibitem{DJS2001}
T.~Damour, P.~Jaranowski, G.~Sch\"afer,
Phys.\ Lett.\ B \textbf{513}, 147 (2001).
[$a_3$, $a_4$ exact]

\bibitem{DJS2015}
T.~Damour, P.~Jaranowski, G.~Sch\"afer,
Phys.\ Rev.\ D \textbf{89}, 064058 (2014).
[$c_{50}^{\pi^4}=2275/512$]

\bibitem{BDG2020_5PN}
D.~Bini, T.~Damour, A.~Geralico,
Phys.\ Rev.\ D \textbf{102}, 024062 (2020) [arXiv:2003.11891].
[5PN--6PN, $c_{51}$ via $\beta^2$]

\bibitem{LMY2024}
M.~Levi, R.~Morales, Z.~Yin,
JHEP (2024). [8.5PN dissipative tail]

\bibitem{spinprec2022}
J.~Blanco-Pillado \textit{et al.}, arXiv:2206.04085 (2022).
[Spin-precession invariant to 9PN; 7PN has numerous transcendentals]

\bibitem{Buonanno1999}
A.~Buonanno, T.~Damour,
Phys.\ Rev.\ D \textbf{59}, 084006 (1999). [EOB framework]

\bibitem{Python2026}
R.~Matshaba, Claude,
\textit{QGD verification suite v3.0}, Python, March 2026.

\end{thebibliography}

\appendix
\section{Ansatz~C Full Tower $n=4$ through $n=9$}

\renewcommand{\arraystretch}{1.2}
\begin{center}
\begin{tabular}{cccccc}
\toprule
$n$ & PN & $\nu^1$ & $\nu^2$ & $\nu^3$ & $\nu^4$ \\
\midrule
4 & 3PN & $-41/32$ & --- & --- & --- \\
5 & 4PN & $+2275/512$ & $+20475/8192$ & --- & --- \\
6 & 5PN & $-5175625/335872$ & $-46580625/5373952$ & $-419225625/85983232$ & --- \\
7 & 6PN & $+11774546875/220332032$ & $\cdots$ & $\cdots$ & $+8583644671875/\ldots$ \\
\bottomrule
\end{tabular}
\end{center}

All entries follow $c_{n,k} = \beta^{2k}c_{n,0}$ with $\beta=-3/4$,
$\beta^2=9/16$, and the sum over $k=0,\ldots,n-4$.

\end{document}
