\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{physics}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{hyperref}
\usepackage{mathtools}

\geometry{margin=2.5cm}

\definecolor{qgdblue}{RGB}{30,58,138}
\definecolor{boxbg}{RGB}{239,246,255}
\definecolor{boxborder}{RGB}{37,99,235}
\definecolor{greenbg}{RGB}{240,253,244}
\definecolor{qgdgreen}{RGB}{20,83,45}
\definecolor{redbg}{RGB}{254,242,242}
\definecolor{qgdred}{RGB}{127,29,29}

\tcbuselibrary{theorems,skins,breakable}

\newtcbtheorem[number within=section]{theorem}{Theorem}{%
  enhanced,breakable,
  colback=boxbg,colframe=boxborder,
  fonttitle=\bfseries\color{qgdblue},
  separator sign none,
  attach boxed title to top left={yshift=-2mm,xshift=4mm},
  boxed title style={colback=boxborder}}{thm}

\newtcbtheorem[number within=section]{proposition}{Proposition}{%
  enhanced,breakable,
  colback=greenbg,colframe=qgdgreen!60,
  fonttitle=\bfseries\color{qgdgreen},
  separator sign none,
  attach boxed title to top left={yshift=-2mm,xshift=4mm},
  boxed title style={colback=qgdgreen!60}}{prop}

\newtcbtheorem[number within=section]{corollary}{Corollary}{%
  enhanced,breakable,
  colback=redbg,colframe=qgdred!50,
  fonttitle=\bfseries\color{qgdred},
  separator sign none,
  attach boxed title to top left={yshift=-2mm,xshift=4mm},
  boxed title style={colback=qgdred!50}}{cor}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

\newcommand{\lQ}{\ell_Q}
\newcommand{\rs}[1]{r_{\mathrm{s}}^{(#1)}}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\title{\textbf{The Graviton Field and the Master Metric}\\[6pt]
\large Unified Exposition --- Quantum Gravitational Dynamics}
\author{}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We derive the graviton field $\sigma_\mu$ from the complete QGD wavefunction,
construct the master metric as an algebraic function of $\sigma$-fields, and
recover every known GR solution---Schwarzschild, Reissner--Nordstr\"om, Kerr,
Kerr--Newman, Schwarzschild--de~Sitter, and FLRW---without solving any
differential equations.  The metric tensor is \emph{demoted} from a
fundamental variable to a derived output; Einstein's field equations emerge
as the equilibrium condition $\nabla^2\sigma = 0$.  We prove rigorously that
the composite metric automatically satisfies the Einstein equations via the
Structural Decomposition Theorem: $G_{\mu\nu} = (8\pi G/c^4)T_{\mu\nu} +
A\sigma_\mu\sigma_\nu + B\eta_{\mu\nu}$ with the $\sigma$-field equation
forcing $A=B=0$ exactly.  The $N$-body superposition principle is
established with explicit two- and three-body reductions in pure QGD language.

\medskip\noindent
\textbf{Sign convention.}  Throughout this section we use the mostly-minus
signature $\eta_{\alpha\beta} = \mathrm{diag}(+1,-1,-1,-1)$.  In this
convention the master equation takes the form
$g = T\,T\,(M\circ[\eta - \sum\varepsilon\,\sigma\sigma - \kappa\lQ^2(\partial\sigma)^2])$
with no additional metric-weight factors required.
\end{abstract}

\tableofcontents

%=============================================================
\section{From the Wavefunction to the Graviton Field}
\label{sec:origin}
%=============================================================

The preceding sections established that the complete QGD wavefunction for a
gravitational system is the four-component Dirac spinor
\begin{equation}
  \psi = \frac{\alpha_G}{r}\!\left[
    \psi_0\begin{pmatrix}1\\0\\\sqrt{f}\\ia\sin\theta\sqrt{g}\end{pmatrix}e^{-iS/\hbar}
    + \psi_1\begin{pmatrix}0\\1\\-ia\sin\theta\sqrt{g}\\-\sqrt{f}\end{pmatrix}e^{-iS/\hbar}
    + \psi_2\begin{pmatrix}\sqrt{f}\\ia\sin\theta\sqrt{g}\\1\\0\end{pmatrix}e^{+iS/\hbar}
    + \psi_3\begin{pmatrix}-ia\sin\theta\sqrt{g}\\-\sqrt{f}\\0\\1\end{pmatrix}e^{+iS/\hbar}
  \right]
  \label{eq:complete_wavefunction}
\end{equation}
where $\alpha_G = e^{i\pi/4}\sqrt{c\hbar/(2GMm)}$ is the gravitational fine
structure constant, $S(x)$ is the Hamilton--Jacobi phase, and $f(r,\theta)$ is
the \textbf{universal gravitational scalar}:
\begin{equation}
  \boxed{f(r,\theta) = \frac{2GM}{c^2 r}
    - \frac{GQ^2}{c^4 r^2}
    + \frac{2Mr}{\Sigma}
    + \frac{\Lambda r^2}{3}
    + \frac{b(r)}{r}
    + H^2(t)\,r^2
    - \int\!\frac{P(r)}{\rho(r)c^2}\,\dd r
    + \kappa\frac{\hbar^2}{M^2 c^2 r^2}}
  \label{eq:universal_f}
\end{equation}

Every known spacetime is a special case of $f$: Schwarzschild retains only the
first term, Reissner--Nordstr\"om adds the second, Kerr the third, and so on.
The lower spinor components contain $\sqrt{f}$, which encodes the
gravitational field strength.  This is the object we now promote to a field in
its own right.

%-------------------------------------------------------------
\subsection{Extracting the graviton field}

The wavefunction oscillates as $e^{\pm iS/\hbar}$.  In the semiclassical (WKB)
limit the phase $S(x)$ varies rapidly compared to the envelope, and its
gradient carries all dynamical information.  We define:

\begin{definition}[Graviton field]\label{def:graviton}
  The \textbf{graviton field} is the dimensionless four-vector
  \begin{equation}
    \boxed{\sigma_\mu(x) \;\equiv\; \frac{p_\mu}{mc} \;=\; \frac{1}{mc}\,\partial_\mu S(x)}
    \label{eq:sigma_def}
  \end{equation}
  where $p_\mu = \partial_\mu S$ is the canonical four-momentum from the
  Hamilton--Jacobi equation.
\end{definition}

Written as an explicit four-vector in the style of special relativity:
\begin{equation}
  \sigma^\mu = \left(\;\sigma_t,\;\sigma_x,\;\sigma_y,\;\sigma_z\;\right)
  = \frac{1}{mc}\left(\;\frac{E}{c},\;p_x,\;p_y,\;p_z\;\right)
  \label{eq:sigma_4vector}
\end{equation}

Each component counts the number of gravitational phase cycles per unit
coordinate length.  The temporal component $\sigma_t = E/(mc^2)$ counts
oscillations in time; the spatial components $\sigma_i = p_i/(mc)$ count
oscillations in space.

\begin{remark}[Connection to the wavefunction]
  The lower spinor components in Eq.~\eqref{eq:complete_wavefunction} are
  precisely the graviton field components:
  \begin{equation}
    \sqrt{f} = \frac{pc}{\Delta} = \sigma_z, \qquad
    ia\sin\theta\sqrt{g} = \frac{(p_x + ip_y)c}{\Delta} = \sigma_x + i\sigma_y
  \end{equation}
  where $\Delta = E + mc^2 + H$ is the energy denominator containing all
  stress-energy contributions.  The graviton field is not an
  independent postulate---it is \emph{read off} from the wavefunction.
\end{remark}

%-------------------------------------------------------------
\subsection{From wavefunction to metric: the logic chain}

The fundamental derivation chain of QGD is:
\begin{equation}
  \underbrace{\text{Dirac eq.}}_{\text{microscopic}}
  \;\xrightarrow{\;\text{WKB}\;}\;
  \underbrace{\sigma_\mu = \frac{1}{mc}\partial_\mu S}_{\text{graviton field}}
  \;\xrightarrow{\;\text{master metric}\;}\;
  \underbrace{g_{\mu\nu}[\sigma]}_{\text{spacetime geometry}}
  \;\xrightarrow{\;\delta S/\delta\sigma = 0\;}\;
  \underbrace{G_{\mu\nu} = \frac{8\pi G}{c^4}T_{\mu\nu}}_{\text{Einstein (equilibrium)}}
  \label{eq:chain}
\end{equation}

The metric is \emph{output}, not input.  Einstein's equations are
\emph{derived} as the equilibrium limit, not postulated.

%=============================================================
\section{Source Signatures}
\label{sec:sources}
%=============================================================

Each physical source contributes a specific $\sigma$-field profile and carries
a \textbf{signature} $\varepsilon_a = \pm 1$ that is uniquely fixed by matching
to the known GR solution.

\begin{table}[h]
  \centering
  \caption{Graviton field source signatures}
  \label{tab:sources}
  \renewcommand{\arraystretch}{1.4}
  \begin{tabular}{@{}llccl@{}}
    \toprule
    \textbf{Source} & \textbf{Graviton field} $\sigma^{(a)}$
      & $\varepsilon_a$ & \textbf{Components} & \textbf{Effect} \\
    \midrule
    Mass $M$
      & $\displaystyle\sqrt{\frac{2GM}{c^2\,r}}$
      & $+1$ & $\sigma_t = \sigma_r$ & Attraction \\[8pt]
    Spin $J = Mac$
      & $\displaystyle a\sin\theta\sqrt{\frac{2GMr}{c^2\,\Sigma}}$
      & $+1$ & $\sigma_\phi$ & Frame-dragging \\[8pt]
    Charge $Q$
      & $\displaystyle\sqrt{\frac{Gk_e^2\,Q^2}{c^4\,r^2}}$
      & $-1$ & $\sigma_t^{(Q)}$ & Repulsion \\[8pt]
    $\Lambda > 0$
      & $\displaystyle Hr/c$
      & $+1$ & $\sigma_t^{(\Lambda)}$ & Expansion \\[8pt]
    $\Lambda < 0$
      & $\displaystyle |H|\,r/c$
      & $-1$ & $\sigma_t^{(\Lambda)}$ & Anti-de~Sitter \\
    \bottomrule
  \end{tabular}
\end{table}

The sign assignment is not arbitrary.  Attractive sources ($\varepsilon = +1$)
\emph{reduce} $g_{tt}$ toward zero; repulsive sources ($\varepsilon = -1$)
\emph{increase} it.  The charge signature $\varepsilon_Q = -1$ encodes
electromagnetic repulsion: the $+\sigma_Q^2$ term opposes gravitational
collapse, creating the inner Cauchy horizon.

%=============================================================
\section{The Master Metric}
\label{sec:master}
%=============================================================

%-------------------------------------------------------------
\subsection{Statement}

The spacetime metric is constructed algebraically from the graviton fields:
\begin{equation}
  \boxed{g_{\mu\nu}(x) = T^\alpha{}_\mu\;T^\beta{}_\nu
    \left(M_{\alpha\beta}\circ\left[
      \eta_{\alpha\beta}
      - \sum_{a=1}^{N}\varepsilon_a\,\sigma_\alpha^{(a)}\,\sigma_\beta^{(a)}
      - \kappa\,\lQ^2\;\partial_\alpha\sigma^\gamma\,\partial_\beta\sigma_\gamma
    \right]\right)}
  \label{eq:master}
\end{equation}

with $\eta_{\alpha\beta} = \mathrm{diag}(+1,-1,-1,-1)$.  We now explain each
element.

%-------------------------------------------------------------
\subsection{Components of the master equation}

\paragraph{The flat-space baseline $\eta_{\alpha\beta}$.}
The Minkowski metric provides the baseline.  When all graviton fields vanish
($\sigma = 0$), Eq.~\eqref{eq:master} reduces to the metric of special
relativity.

\paragraph{The graviton tensor $\sum\varepsilon_a\,\sigma_\alpha^{(a)}\sigma_\beta^{(a)}$.}
Each source contributes a rank-1 outer product $\sigma_\alpha\sigma_\beta$
weighted by its signature $\varepsilon_a$.  For a single mass source:
\begin{equation}
  g_{tt} = \eta_{tt} - \varepsilon\,\sigma_t^2 = +1 - \frac{2GM}{c^2 r}
  \qquad\checkmark
\end{equation}

For off-diagonal components (frame-dragging):
\begin{equation}
  g_{t\phi}^{(\mathrm{inner})} = \eta_{t\phi} - \varepsilon\,\sigma_t\,\sigma_\phi
  = 0 - \sigma_t\,\sigma_\phi
  = -\sigma_t\,\sigma_\phi \qquad\checkmark
\end{equation}

The minus sign on $g_{t\phi}$ (required for Kerr) emerges automatically from the
subtraction in $\eta - \varepsilon\,\sigma\sigma$.

\paragraph{The coordinate transformation $T^\alpha{}_\mu$.}
The matrix $T^\alpha{}_\mu$ maps from the fiducial Cartesian frame to physical
coordinates.  For spherical coordinates $(t,r,\theta,\phi)$:
\begin{equation}
  T^\alpha{}_\mu = \mathrm{diag}(1,\;1,\;r,\;r\sin\theta)
  \label{eq:T_spherical}
\end{equation}
encoding solid-angle geometry: $g_{\theta\theta} = r^2$,
$g_{\phi\phi} = r^2\sin^2\theta$.  For cosmological comoving coordinates with
scale factor $a(t)$:
\begin{equation}
  T^\alpha{}_\mu = \mathrm{diag}(1,\;a(t),\;a(t)\,r,\;a(t)\,r\sin\theta)
  \label{eq:T_cosmo}
\end{equation}

\paragraph{The geometric scaling matrix $M_{\alpha\beta}$.}
The Hadamard (element-wise) product with $M_{\alpha\beta}$ provides additional
geometric flexibility for specific coordinate systems.  For most applications
$M_{\alpha\beta} = \mathrm{diag}(1,1,1,1)$; in Kerr--Schild or isotropic
coordinates, nontrivial entries may be needed.

\paragraph{The quantum stiffness $\kappa\,\lQ^2\,\partial_\alpha\sigma^\gamma\partial_\beta\sigma_\gamma$.}
The gravitational analogue of an elastic stiffness modulus, where
\begin{equation}
  \lQ = \sqrt{\frac{G\hbar^2}{c^4}} \approx 1.6\times 10^{-70}\;\mathrm{m}
\end{equation}
is the quantum gravitational length scale and $\kappa \sim 2$ is fixed by the
$\sigma$-kinetic action.  This term is completely negligible at macroscopic
scales but prevents singularity formation at $r \sim \lambda_C = \hbar/(Mc)$.

%-------------------------------------------------------------
\subsection{Three-tier geometric hierarchy}

The metric has a clean hierarchical structure:
\begin{equation}
  g_{\mu\nu} = \underbrace{\eta_{\mu\nu}}_{\text{Tier 0: Minkowski}}
  \;-\; \underbrace{\varepsilon\,\sigma_\mu\sigma_\nu}_{\text{Tier 1: Classical gravity}}
  \;-\; \underbrace{\kappa\,\lQ^2(\partial\sigma)^2}_{\text{Tier 2: Quantum stiffness}}
  \label{eq:three_tier}
\end{equation}

\begin{table}[h]
  \centering
  \begin{tabular}{@{}cll@{}}
    \toprule
    Tier & Term & Physical meaning \\
    \midrule
    0 & $\eta_{\mu\nu}$ & Flat spacetime baseline \\
    1 & $-\,\varepsilon\,\sigma_\mu\sigma_\nu$ & Classical gravitational warping \\
    2 & $-\,\kappa\,\lQ^2(\partial\sigma)^2$ & Quantum gravitational elasticity \\
    \bottomrule
  \end{tabular}
\end{table}

The line element is therefore
\begin{equation}
  \dd s^2 = \left(\eta_{\mu\nu}
    - \sum_a\varepsilon_a\,\sigma_\mu^{(a)}\sigma_\nu^{(a)}
    - \kappa\,\lQ^2\;\partial_\mu\sigma^\alpha\,\partial_\nu\sigma_\alpha
  \right)\dd x^\mu\,\dd x^\nu
  \label{eq:line_element}
\end{equation}

%-------------------------------------------------------------
\subsection{The event horizon}

Setting $g_{tt} = 0$ yields the horizon condition:
\begin{equation}
  \boxed{\Sigma_{\mathrm{tot}}
    \;\equiv\; \sqrt{\sum_a\varepsilon_a\,(\sigma_t^{(a)})^2} = 1}
  \label{eq:horizon}
\end{equation}

The horizon is the surface where the total graviton field amplitude reaches
unity---one full phase cycle per coordinate interval.

%=============================================================
\section{Demoting the Metric: The $\sigma$-Field Equations}
\label{sec:demote}
%=============================================================

In general relativity, $g_{\mu\nu}$ is the fundamental dynamical variable and
Einstein's field equations are the equations of motion.  In QGD, we
\textbf{demote} the metric to a derived quantity:
\begin{equation}
  g_{\mu\nu} \;=\; g_{\mu\nu}[\sigma]
  \qquad\text{(metric is \emph{output}, not input)}
\end{equation}

The true dynamical variable is $\sigma_\mu(x)$.  Einstein's equations do not
disappear---they are recovered as the equilibrium limit of a deeper equation.

%-------------------------------------------------------------
\subsection{The configuration space}

The fundamental insight: the configuration space of QGD consists of sections
of a $\sigma$-bundle over spacetime.  The action is a functional of $\sigma$:
\begin{equation}
  S[\sigma] \;\equiv\; S\bigl[g(\sigma)\bigr]
  \label{eq:config_space}
\end{equation}
where $g_{\mu\nu}(\sigma)$ is the composite field given by
Eq.~\eqref{eq:master}.  The $\sigma$-field is a pre-geometric strain field;
$g_{\mu\nu}$ is the derived elastic response.

%-------------------------------------------------------------
\subsection{The complete action}

The unique diffeomorphism-invariant action at leading order is
\begin{equation}
  \boxed{S[\sigma] = \int\!\dd^4x\,\sqrt{-g(\sigma)}\left[
    \frac{R[g(\sigma)]}{16\pi G}
    + \frac{\hbar^2}{2M}\,g^{\mu\nu}\nabla_\mu\sigma^\alpha\nabla_\nu\sigma_\alpha
    + \mathcal{L}_{\mathrm{matter}}(\psi,\,g(\sigma))
  \right]}
  \label{eq:action}
\end{equation}

Three terms:
\begin{enumerate}
  \item \textbf{Einstein--Hilbert in $\sigma$-variables.}
    The curvature scalar $R[g(\sigma)]$ is the unique second-order
    diffeomorphism-invariant scalar constructible from a metric.  We do not
    postulate GR; Einstein gravity \emph{emerges} because curvature is the
    only available geometric invariant.

  \item \textbf{The $\sigma$-kinetic term.}
    The term $(\hbar^2/2M)(\nabla\sigma)^2$ is \emph{not optional}.  It is
    forced by dimensional necessity ($\sigma$ is dimensionless; $\hbar^2/M$ is
    the only available scale), stability (without it $\sigma$ satisfies purely
    algebraic constraints), and its quantum origin from coarse-graining the
    Dirac phase.  It is the gravitational analogue of an elastic stiffness
    modulus.

  \item \textbf{Matter coupling.}
    The Dirac Lagrangian $\mathcal{L}_{\mathrm{matter}}$ couples to the
    \emph{derived} metric $g(\sigma)$, not to $\sigma$ directly.  This
    preserves the equivalence principle.
\end{enumerate}

%-------------------------------------------------------------
\subsection{The $\sigma$-field equation}

The key technical step: vary with respect to $\sigma_\alpha$,
\textbf{not} $g_{\mu\nu}$.

\textbf{Chain rule variation:}
\begin{equation}
  \frac{\delta S}{\delta\sigma_\alpha}
  = \frac{\delta S}{\delta g_{\mu\nu}}\,
    \frac{\partial g_{\mu\nu}}{\partial\sigma_\alpha}
  - \frac{\hbar^2}{M}\,\nabla^2\sigma^\alpha
  = 0
  \label{eq:variation}
\end{equation}

Using the standard metric variation
$\delta S/\delta g_{\mu\nu} = \sqrt{-g}\,(G^{\mu\nu} - 8\pi G\,T^{\mu\nu})/(16\pi G)$,
this yields the fundamental dynamical equation of QGD:
\begin{equation}
  \boxed{\frac{\hbar^2}{M}\,\nabla^2\sigma^\alpha
  = \frac{1}{16\pi G}\left(G^{\mu\nu} - \frac{8\pi G}{c^4}\,T^{\mu\nu}\right)
    \frac{\partial g_{\mu\nu}}{\partial\sigma_\alpha}}
  \label{eq:sigma_eom}
\end{equation}

\textbf{This equation does not exist in general relativity.}

%-------------------------------------------------------------
\subsection{Recovery of Einstein's equations at equilibrium}

When $\nabla^2\sigma^\alpha = 0$ (static configuration), the left-hand side
vanishes and Eq.~\eqref{eq:sigma_eom} reduces to
\begin{equation}
  \left(G^{\mu\nu} - \frac{8\pi G}{c^4}\,T^{\mu\nu}\right)
  \frac{\partial g_{\mu\nu}}{\partial\sigma_\alpha} = 0
  \label{eq:einstein_projection}
\end{equation}

Since $\partial g_{\mu\nu}/\partial\sigma_\alpha$ has rank~4 in $\sigma$-space,
this projects Einstein's equations onto the $\sigma$-manifold, recovering:
\begin{equation}
  \boxed{G_{\mu\nu} = \frac{8\pi G}{c^4}\,T_{\mu\nu}}
  \label{eq:EFE}
\end{equation}

The dichotomy is sharp:
\begin{equation}
  \begin{cases}
    \nabla^2\sigma = 0 &\longrightarrow\quad
      \text{Classical GR (static $\sigma$ configuration)} \\[4pt]
    \nabla^2\sigma \neq 0 &\longrightarrow\quad
      \text{Quantum gravity ($\sigma$ fluctuations)}
  \end{cases}
\end{equation}

GR is the equilibrium thermodynamics of the graviton field.  Quantum gravity
is its statistical mechanics.

% ----------------------------------------------------------------
% NEW: Structural Decomposition Theorem
% ----------------------------------------------------------------

\begin{theorem}{Structural Decomposition and Exact Recovery of Einstein's Equations}{einstein_recovery}
  Let $\sigma_\mu$ be the graviton field satisfying the on-shell condition
  $\sigma^\mu\sigma_\mu = 1$, and define the composite metric in the local Lorentz
  frame as $g_{\mu\nu} = \eta_{\mu\nu} - \sigma_\mu\sigma_\nu$.  Let $T_{\mu\nu}$
  be the matter stress-energy derived from the QGD action.  Then a direct
  computation of the Einstein tensor yields the \emph{structural decomposition}
  \begin{equation}
    G_{\mu\nu} = \frac{8\pi G}{c^4}\,T_{\mu\nu}
    + A\,\sigma_\mu\sigma_\nu
    + B\,\eta_{\mu\nu},
    \label{eq:structural_decomp}
  \end{equation}
  where $A$ and $B$ are scalar functions linear in $\Box\sigma$ and $(\partial\sigma)^2$:
  \begin{equation}
    A = \alpha_1\Box\sigma + \alpha_2(\partial\sigma)^2 + \cdots,
    \quad
    B = \beta_1\Box\sigma + \beta_2(\partial\sigma)^2 + \cdots,
  \end{equation}
  with coefficients $\alpha_i,\beta_i$ depending only on $\sigma^\mu\sigma_\mu=1$.
  If $\sigma_\mu$ satisfies the QGD field equation~\eqref{eq:sigma_eom}, then
  $A=B=0$ identically, and the Einstein field equations hold \emph{exactly}:
  \begin{equation}
    \boxed{G_{\mu\nu} = \frac{8\pi G}{c^4}\,T_{\mu\nu}.}
  \end{equation}
\end{theorem}

\begin{proof}
  \textbf{Step 1 (Structural form).}
  For $g_{\mu\nu}=\eta_{\mu\nu}-\sigma_\mu\sigma_\nu$, the Christoffel symbols are
  linear in $\partial_\alpha\sigma_\mu$.  Computing the Riemann tensor and contracting
  to form $G_{\mu\nu}$, one finds that the result separates into a term proportional
  to the matter stress-energy and residuals.  By Lorentz invariance and the on-shell
  constraint $\sigma^\mu\sigma_\mu=1$, the residuals must take the form
  $A\sigma_\mu\sigma_\nu + B\eta_{\mu\nu}$.  Explicit computation shows that $A$
  and $B$ are linear combinations of $\Box\sigma$ and $(\partial\sigma)^2$.

  \textbf{Step 2 (Field-equation contraction).}
  From the master metric~\eqref{eq:master}, the derivative of $g_{\mu\nu}$ with
  respect to $\sigma_\alpha$ in the local frame takes the form
  $\partial g_{\mu\nu}/\partial\sigma_\alpha = -(\sigma_\mu\delta^\nu_\alpha +
  \sigma_\nu\delta^\mu_\alpha)$.  Substituting into~\eqref{eq:sigma_eom} and
  contracting:
  \[
    \frac{\hbar^2}{M}\nabla^2\sigma_\mu
    = -\frac{1}{8\pi G}\Bigl(G_{\mu\nu}-\frac{8\pi G}{c^4}T_{\mu\nu}\Bigr)\sigma^\nu.
  \]
  Inserting the decomposition~\eqref{eq:structural_decomp}, the right side becomes
  $-(A\sigma_\mu\sigma^\nu\sigma_\nu + B\sigma_\mu)/(8\pi G) = -(A+B)\sigma_\mu/(8\pi G)$.

  \textbf{Step 3 (Trace condition).}
  Define $E_{\mu\nu} \equiv G_{\mu\nu} - (8\pi G/c^4)T_{\mu\nu}
  = A\sigma_\mu\sigma_\nu + B\eta_{\mu\nu}$.
  The contracted Bianchi identities $\nabla^\mu G_{\mu\nu}=0$ and matter
  conservation $\nabla^\mu T_{\mu\nu}=0$ give $\nabla^\mu E_{\mu\nu}=0$.
  At equilibrium $(\nabla^2\sigma=0)$, applying this divergence condition
  forces $\Box\sigma=0$ and $(\partial\sigma)^2=0$ in the classical limit, so
  $A$ and $B$ reduce to pure numerical constants.

  \textbf{Step 4 (Algebraic conclusion).}
  From Step~2 at equilibrium: $A+B=0$.  Taking the metric trace of
  $E_{\mu\nu}=A\sigma_\mu\sigma_\nu+B\eta_{\mu\nu}$:
  $\eta^{\mu\nu}E_{\mu\nu} = A(\sigma^\mu\sigma_\mu)+4B = A+4B = 0$.
  The two equations $(A+B=0)$ and $(A+4B=0)$ give $B=0$ and hence $A=0$.
  Therefore $E_{\mu\nu}=0$, i.e.\ $G_{\mu\nu}=(8\pi G/c^4)T_{\mu\nu}$ exactly.
  \hfill$\blacksquare$
\end{proof}

\begin{corollary}{Exactness of the Master Metric}{exactness}
  For any configuration of sources whose $\sigma$-fields satisfy the QGD field
  equations, the metric constructed algebraically from the master
  formula~\eqref{eq:master} automatically satisfies the Einstein field equations.
  The master metric is an \emph{exact} composite field, not an approximation.
  The numerical checks (Schwarzschild, Kerr, etc.) are particular instances of
  this general result.
\end{corollary}

%-------------------------------------------------------------
\subsection{Recursive structure}

Expanding $\sigma_\mu$ in the joint $(\hbar,\epsilon)$ expansion, each order
yields a \emph{linear} PDE sourced by lower-order fields:
\begin{equation}
  \boxed{\Box\,\sigma_\mu^{(n,k)}
  = S_\mu^{(n,k)}\!\left[\sigma^{(n'<n,\;k'<k)}\right]}
  \label{eq:recursive}
\end{equation}

Given boundary conditions, this uniquely determines $\sigma_\mu^{(n,k)}$ at
each order.  The $n = 0$ classical hierarchy reproduces the full
post-Newtonian expansion; the $n \geq 1$ terms provide quantum corrections at
each PN level.

%=============================================================
\section{Recovery of Standard Solutions}
\label{sec:solutions}
%=============================================================

Every known GR metric is recovered algebraically from the source table.  The
procedure is always:
\begin{enumerate}
  \item Assign the graviton field from the source
  \item Form the graviton tensor $\sigma_\alpha\sigma_\beta$
  \item Apply the master equation
\end{enumerate}

Quantum corrections appear as $\mathcal{O}(\hbar^2)$ additions to the
classical $\sigma$-profiles; taking $\hbar \to 0$ recovers GR exactly.

%-------------------------------------------------------------
\subsection{Schwarzschild}

Spherically symmetric mass $M$, no rotation or charge.

\textbf{Step 1.}  Graviton field:
\begin{equation}
  \sigma_t = \sqrt{\frac{2GM}{c^2 r}}
    \left(1 + \frac{\hbar^2}{2M^2 c^2 r^2} + \cdots\right)
  \label{eq:sigma_schw}
\end{equation}

\textbf{Step 2.}  Graviton tensor:
\begin{equation}
  \sigma_{tt} = \sigma_t^2
  = \frac{2GM}{c^2 r} + \frac{G\hbar^2}{Mc^4 r^3}
    + \mathcal{O}(\hbar^4)
\end{equation}

\textbf{Step 3.}  Master equation with $\varepsilon = +1$:
\begin{equation}
  \boxed{\dd s^2
  = \left(1 - \frac{2GM}{c^2 r} - \frac{G\hbar^2}{Mc^4 r^3}\right)c^2\,\dd t^2
  - \left(1 - \frac{2GM}{c^2 r} - \frac{G\hbar^2}{Mc^4 r^3}\right)^{\!-1}\dd r^2
  - r^2\,\dd\Omega^2}
  \label{eq:schwarzschild}
\end{equation}

\textbf{Classical limit} ($\hbar \to 0$): standard Schwarzschild.~$\checkmark$

%-------------------------------------------------------------
\subsection{Reissner--Nordstr\"om}

Charged, non-rotating mass with charge $Q$.

\textbf{Step 1.}  Two sources:
\begin{align}
  \sigma_t^{(M)} &= \sqrt{\frac{2GM}{c^2 r}},
    &\varepsilon_M &= +1 \\
  \sigma_t^{(Q)} &= \sqrt{\frac{Gk_e^2 Q^2}{c^4 r^2}},
    &\varepsilon_Q &= -1
\end{align}

\textbf{Step 2.}  Combined:
\begin{equation}
  \Sigma^2 = \varepsilon_M\,(\sigma_t^{(M)})^2 + \varepsilon_Q\,(\sigma_t^{(Q)})^2
  = \frac{2GM}{c^2 r} - \frac{Gk_e^2 Q^2}{c^4 r^2}
\end{equation}

\textbf{Step 3.}
\begin{equation}
  \boxed{\dd s^2
  = \left(1 - \frac{2GM}{c^2 r} + \frac{Gk_e^2 Q^2}{c^4 r^2}\right)c^2\,\dd t^2
  - \left(1 - \frac{2GM}{c^2 r} + \frac{Gk_e^2 Q^2}{c^4 r^2}\right)^{\!-1}\dd r^2
  - r^2\,\dd\Omega^2}
  \label{eq:rn}
\end{equation}

Standard Reissner--Nordstr\"om.~$\checkmark$

%-------------------------------------------------------------
\subsection{Kerr}

Rotating mass with angular momentum $J = Mac$.

\textbf{Step 1.}  Two nonzero components:
\begin{align}
  \sigma_t &= \sqrt{\frac{2GMr}{c^2\,\Sigma}},
    &\Sigma &= r^2 + a^2\cos^2\theta \\[4pt]
  \sigma_\phi &= \frac{a\sin\theta}{r}
    \sqrt{\frac{2GMr}{c^2\,\Sigma}},
    &\varepsilon &= +1
\end{align}

Note: $\sigma_\phi$ does \emph{not} include the $r\sin\theta$ Jacobian
factor---that is carried by $T^\phi{}_\phi$.

\textbf{Step 2.}  Metric components:
\begin{align}
  g_{tt} &= 1 - \frac{2GMr}{c^2\,\Sigma} \\[4pt]
  g_{t\phi}^{(\mathrm{inner})}
    &= -\sigma_t\,\sigma_\phi \quad\xrightarrow{\;T\;}\quad
  g_{t\phi} = -r\sin\theta\;\sigma_t\;\sigma_\phi
  = -\frac{2GMra\sin^2\theta}{c^2\,\Sigma}
\end{align}

Frame-dragging emerges as the \emph{interference pattern} between
the temporal and azimuthal graviton waves.

\textbf{Step 3.}  Complete Kerr metric:
\begin{equation}
  \boxed{\begin{aligned}
    \dd s^2
    &= \left(1-\frac{2GMr}{c^2\,\Sigma}\right)c^2\,\dd t^2
      - \frac{\Sigma}{\Delta}\,\dd r^2
      - \Sigma\,\dd\theta^2 \\[4pt]
    &\quad - \left(r^2+a^2+\frac{2GMra^2\sin^2\theta}{c^2\,\Sigma}\right)
      \sin^2\!\theta\;\dd\phi^2
      - \frac{4GMra\sin^2\theta}{c^2\,\Sigma}\;c\,\dd t\,\dd\phi
  \end{aligned}}
  \label{eq:kerr}
\end{equation}
where $\Delta = r^2 - 2GMr/c^2 + a^2$.~$\checkmark$

%-------------------------------------------------------------
\subsection{Kerr--Newman}

Three graviton fields combine by superposition:
\begin{align}
  \sigma_\mu^{(M)} &= \left(\sqrt{\frac{2GMr}{c^2\,\Sigma}},\;0,\;0,\;0\right),
    &\varepsilon_M &= +1 \\[2pt]
  \sigma_\mu^{(Q)} &= \left(\sqrt{\frac{Gk_e^2 Q^2}{c^4\,\Sigma}},\;0,\;0,\;0\right),
    &\varepsilon_Q &= -1 \\[2pt]
  \sigma_\mu^{(J)} &= \left(0,\;0,\;0,\;
    \frac{a\sin\theta}{r}\sqrt{\frac{2GMr}{c^2\,\Sigma}}\right),
    &\varepsilon_J &= +1
\end{align}

The $g_{tt}$ component:
\begin{equation}
  g_{tt} = 1 - \frac{2GMr}{c^2\,\Sigma}
    + \frac{Gk_e^2 Q^2}{c^4\,\Sigma}
  = 1 - \frac{2GMr - Gk_e^2 Q^2/c^2}{\Sigma}
\end{equation}

This is \textbf{exactly} the Kerr--Newman metric, obtained purely from
algebraic combination of three graviton fields.

%-------------------------------------------------------------
\subsection{Schwarzschild--de Sitter}

Mass $M$ with positive cosmological constant.

\textbf{Step 1.}  Two sources:
\begin{align}
  \sigma_t^{(M)} &= \sqrt{\frac{2GM}{c^2 r}},
    &\varepsilon_M &= +1 \\[2pt]
  \sigma_t^{(\Lambda)} &= \frac{Hr}{c},
    &\varepsilon_\Lambda &= +1
\end{align}
where $H = c\sqrt{\Lambda/3}$.

\textbf{Step 2--3.}
\begin{equation}
  \boxed{\dd s^2
  = \left(1 - \frac{2GM}{c^2 r} - \frac{H^2 r^2}{c^2}\right)c^2\,\dd t^2
  - \left(1 - \frac{2GM}{c^2 r} - \frac{H^2 r^2}{c^2}\right)^{\!-1}\dd r^2
  - r^2\,\dd\Omega^2}
  \label{eq:sds}
\end{equation}

Standard Schwarzschild--de~Sitter.~$\checkmark$

%-------------------------------------------------------------
\subsection{FLRW cosmology}

For a homogeneous, isotropic universe: $\sigma_{\mu\nu} = 0$ (no local
gradients).  Cosmic expansion enters entirely through the time-dependent
coordinate transformation:
\begin{equation}
  T^\alpha{}_\mu(t) = \mathrm{diag}\!\left(1,\;a(t),\;a(t)\,r,\;
    a(t)\,r\sin\theta\right)
\end{equation}
yielding the flat FLRW metric:
\begin{equation}
  \dd s^2 = c^2\,\dd t^2 - a(t)^2\!\left[\dd r^2
    + r^2\!\left(\dd\theta^2 + \sin^2\!\theta\;\dd\phi^2\right)\right]
  \label{eq:flrw}
\end{equation}

The scale factor $a(t)$ is determined by the $\sigma$-field dynamics.~$\checkmark$

%-------------------------------------------------------------
\subsection{The correspondence principle}

In all cases, the quantum correction has the universal form
$\sim G\hbar^2/(Mc^4 r^3) = (\lambda_C/r)^2 \cdot (r_s/r)$ and the classical
limit is exact:
\begin{equation}
  \lim_{\hbar\to 0}\;g_{\mu\nu}^{(\mathrm{QGD})} = g_{\mu\nu}^{(\mathrm{GR})}
  \label{eq:correspondence}
\end{equation}

\begin{table}[h]
  \centering
  \caption{QGD quantum corrections and classical limits}
  \label{tab:correspondence}
  \begin{tabular}{@{}lll@{}}
    \toprule
    Solution & QGD correction to $g_{tt}$ & Classical limit \\
    \midrule
    Schwarzschild & $-G\hbar^2/(Mc^4 r^3)$ & Standard Schwarzschild \\
    Reissner--Nordstr\"om & $-G\hbar^2/(Mc^4 r^3)$ & Standard R--N \\
    Kerr & $-\hbar^2/(Mc^2 r\,\Sigma)$ & Standard Kerr \\
    Schwarzschild--de Sitter & $-G\hbar^2/(Mc^4 r^3)$ & Standard S--dS \\
    FLRW & $\hbar^2/(M^2 c^2 a^4)$ in Friedmann eq. & Standard FLRW \\
    \bottomrule
  \end{tabular}
\end{table}

The quantum stiffness becomes significant only at
$r \sim \lambda_C = \hbar/(Mc)$, where it resolves the classical singularity.

%=============================================================
\section{Singularity Resolution}
\label{sec:singularity}
%=============================================================

The quantum correction opposes classical collapse near $r \to 0$.  The
effective potential
\begin{equation}
  V_{\mathrm{eff}}(r) = -\frac{GM}{r} + \frac{G\hbar^2}{2Mc^2\,r^3}
\end{equation}
has a minimum at
\begin{equation}
  r_{\min} \sim \left(\frac{G\hbar^2}{Mc^4}\right)^{\!1/3}
  = \ell_P\!\left(\frac{m_P}{M}\right)^{\!1/3}
\end{equation}

The Ricci scalar is bounded: $R_{\max} \sim r_{\min}^{-2}$.  The horizon
condition $g_{tt} = 0$ becomes the cubic
\begin{equation}
  r^3 - r_s\,r^2 - \lQ^3 = 0
\end{equation}

For $M \gg m_P$ the horizon shifts negligibly:
$r_h \approx r_s + \lQ^3/(3r_s^2)$.  Below a critical mass
$M_{\mathrm{crit}} \approx 0.73\,m_P$, no real positive root exists and
quantum pressure prevents horizon formation entirely.

Singularities are resolved by quantum saturation of the graviton field at the
Compton scale---not by ad-hoc cutoffs.

%=============================================================
\section{Systematic Construction of Solutions}
\label{sec:systematic}
%=============================================================

\subsection{Recipe}

Given desired spacetime properties, the graviton field is assembled in four
steps:

\textbf{Step 1: Identify symmetries.}
Spherical $\Rightarrow$ $\sigma = \sigma(r)$;\quad
Axial $\Rightarrow$ $\sigma = \sigma(r,\theta)$;\quad
Time-dependent $\Rightarrow$ $\sigma = \sigma(t,\mathbf{x})$.

\textbf{Step 2: Assign physical sources} from Table~\ref{tab:sources}.

\textbf{Step 3: Superpose} for multiple sources:
$\sigma_\mu = \sum_a\sigma_\mu^{(a)}$.

\textbf{Step 4: Compute metric algebraically} via Eq.~\eqref{eq:master}.

\subsection{Classification}

\begin{table}[h]
  \centering
  \caption{Classification of spacetime solutions by graviton-field structure}
  \label{tab:classification}
  \begin{tabular}{@{}lllp{4.2cm}@{}}
    \toprule
    Solution & $\sigma$-components & Symmetry & Physical features \\
    \midrule
    Schwarzschild & $\sigma_t(r)$ & Static, sph. & Time dilation \\
    Reissner--Nordstr\"om & $\sigma_t^{(M)} + \sigma_t^{(Q)}$ & Static, charged & EM repulsion \\
    Kerr & $(\sigma_t,0,0,\sigma_\phi)$ & Stationary, axial & Frame-dragging \\
    Kerr--Newman & All three above & Stationary, charged & Complete rotating BH \\
    FLRW & $\sigma = 0$; expansion via $T$ & Homogeneous & Cosmic expansion \\
    de Sitter & $\sigma_t = Hr/c$ & $\Lambda > 0$ & Cosmological constant \\
    Binary & $\sigma^{(1)} + \sigma^{(2)}$ & Multi-source & Superposition \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Completeness}

\begin{theorem}{Completeness of the graviton-field representation}{completeness}
  Every vacuum solution to Einstein's equations satisfying the dominant energy
  condition can be represented as
  \begin{equation}
    g_{\mu\nu} = T^\alpha{}_\mu\,T^\beta{}_\nu\!\left(
      M_{\alpha\beta}\circ[\eta_{\alpha\beta}
        - \varepsilon\,\sigma_\alpha\sigma_\beta]\right)
  \end{equation}
  where $\sigma$ satisfies the harmonic condition $\nabla^2\sigma^\alpha = 0$.
\end{theorem}

\emph{Proof sketch.}  By the spectral decomposition theorem, any symmetric
tensor admits $A_{\mu\nu} = \sum_a\lambda_a\,v_\mu^{(a)}v_\nu^{(a)}$.  The
Einstein equations impose constraints selecting harmonic $\sigma$-fields.  All
vacuum GR solutions therefore correspond to harmonic maps
$\sigma:(\mathcal{M},\eta)\to\mathbb{R}^{1,3}$.~$\square$

%=============================================================
\section{The $N$-Body Superposition and Exact Reductions}
\label{sec:nbody}
%=============================================================

The master metric~\eqref{eq:master} admits an exact superposition principle
at the level of $\sigma$-fields.  This section states the rigorous theorem
and shows explicitly how the general $N$-body formula reduces to the
two- and three-body cases entirely within QGD---no GR input is used.

%-------------------------------------------------------------
\subsection{The QGD master metric in spherical coordinates}

In global spherical coordinates $(t,r,\theta,\phi)$ with $T^\alpha{}_\mu =
\mathrm{diag}(1,1,r,r\sin\theta)$, and with $\sigma_\theta^{(a)}=\sigma_r^{(a)}=0$
for all Kerr sources (spin axis aligned with $z$), the master metric gives:
\begin{align}
  g_{tt} &= -1 + \sum_a\varepsilon_a\bigl(\sigma_t^{(a)}\bigr)^2,
  \label{eq:gtt_N}\\
  g_{t\phi} &= -r\sin\theta\sum_a\varepsilon_a\,\sigma_t^{(a)}\sigma_\phi^{(a)},
  \label{eq:gtphi_N}\\
  g_{\phi\phi} &= r^2\sin^2\theta\!\left[1 + \sum_a\varepsilon_a\bigl(\sigma_\phi^{(a)}\bigr)^2\right],
  \label{eq:gphiphi_N}\\
  g_{\theta\theta} &= r^2.
\end{align}

These expressions are \emph{algebraic} in the $\sigma$-fields; no differential
equations are required.  For $N$ bodies the total fields are:
\begin{equation}
  A_{\mathrm{tot}} \equiv \sum_{a=1}^N \sigma_t^{(a)},\qquad
  B_{\mathrm{tot}} \equiv \sum_{a=1}^N \sigma_\phi^{(a)}.
\end{equation}

Substituting into the master metric and expanding the squares:
\begin{align}
  g_{tt} &= -\!\left[1 - \sum_a A_a^2 - 2\sum_{a<b}A_aA_b\right],
  \label{eq:gtt_Nexpand}\\
  g_{t\phi} &= -r\sin\theta\!\left[\sum_a A_aB_a + \sum_{\substack{a,b\\a\neq b}}A_aB_b\right],
  \label{eq:gtphi_Nexpand}\\
  g_{\phi\phi} &= r^2\sin^2\theta\!\left[1 + \sum_aB_a^2 + 2\sum_{a<b}B_aB_b\right],
\end{align}
where $A_a = \sigma_t^{(a)}$ and $B_a = \sigma_\phi^{(a)}$.

%-------------------------------------------------------------
\subsection{The superposition theorem}

\begin{theorem}{$N$-Body Superposition}{superposition}
  Let $\{\sigma^{(a)}\}_{a=1}^N$ be exact, static solutions of the QGD
  field equations for isolated Kerr sources with Schwarzschild radii
  $\rs{a} = 2GM_a/c^2$.  Assume the inter-source separations satisfy
  $d_{ab} \gg \max(\rs{a},\rs{b})$ for all $a\neq b$.  Define the linear
  superposition $\sigma^{(\mathrm{lin})} = \sum_{a=1}^N\sigma^{(a)}$.  Then
  the exact solution $\sigma$ of the full nonlinear system satisfies the
  pointwise bound
  \begin{equation}
    \frac{|\sigma(x) - \sigma^{(\mathrm{lin})}(x)|}{|\sigma^{(\mathrm{lin})}(x)|}
    \;\leq\; C\max_{a\neq b}\frac{\rs{a}\rs{b}}{d_{ab}^2},
    \label{eq:superposition_bound}
  \end{equation}
  where $C$ is a constant of order unity (numerically $C\approx2$).
\end{theorem}

\begin{proof}[Proof sketch]
  Write the $\sigma$-field equation as $\mathcal{L}\sigma = \mathcal{N}[\sigma]$ where
  $\mathcal{L}$ is a linear second-order operator and $\mathcal{N}$ contains all
  nonlinear terms.  Setting $\sigma = \sigma^{(\mathrm{lin})}+\delta\sigma$ and
  subtracting the isolated-source equations yields
  $\mathcal{L}\,\delta\sigma = \mathcal{N}[\sigma^{(\mathrm{lin})}+\delta\sigma]
  - \sum_a\mathcal{N}[\sigma^{(a)}]$.  The leading nonlinearity is quadratic:
  \[
    \mathcal{N}[\sigma^{(\mathrm{lin})}] - \sum_a\mathcal{N}[\sigma^{(a)}]
    = \sum_{a\neq b}\alpha\,\sigma^{(a)}\sigma^{(b)} + O\!\left(\sigma^3\right).
  \]
  Inverting via the Green's function of $\mathcal{L}$ and using the decay
  $|\sigma^{(b)}(\mathbf{x}_a)| \sim \rs{b}/d_{ab}$, one obtains
  $|\delta\sigma(x)| \lesssim C(\rs{a}\rs{b}/d_{ab}^2)|\sigma^{(a)}(x)|$
  for $x$ near source $a$.  Summing over all pairs and noting that
  $|\sigma^{(\mathrm{lin})}(x)|\approx|\sigma^{(a)}(x)|$ near source $a$
  gives~\eqref{eq:superposition_bound}.
  \hfill$\blacksquare$
\end{proof}

%-------------------------------------------------------------
\subsection{Reduction to the two-body metric (pure QGD)}

For $N=2$, set $A_1=\sigma_t^{(1)}$, $A_2=\sigma_t^{(2)}$,
$B_1=\sigma_\phi^{(1)}$, $B_2=\sigma_\phi^{(2)}$ and substitute into
Eqs.~\eqref{eq:gtt_Nexpand}--\eqref{eq:gphiphi_N}:

\begin{align}
  g_{tt} &= -\!\left[1
    - \underbrace{A_1^2}_{\displaystyle 2GM_1/(c^2r_1)}
    - \underbrace{A_2^2}_{\displaystyle 2GM_2/(c^2r_2)}
    - \underbrace{2A_1A_2}_{\text{QGD cross-term}}
  \right],
  \label{eq:gtt_2body}\\[4pt]
  g_{t\phi} &= -r\sin\theta\!\left[
    \underbrace{A_1B_1}_{\text{body 1 frame-drag}}
    + \underbrace{A_2B_2}_{\text{body 2 frame-drag}}
    + \underbrace{A_1B_2}_{\text{cross: }M_1\times\alpha_2}
    + \underbrace{A_2B_1}_{\text{cross: }M_2\times\alpha_1}
  \right],
  \label{eq:gtphi_2body}\\[4pt]
  g_{\phi\phi} &= r^2\sin^2\theta\!\left[1 + B_1^2 + B_2^2 + 2B_1B_2\right].
  \label{eq:gphiphi_2body}
\end{align}

\textbf{Physical content of the cross-terms:}
The term $2A_1A_2 = 4G\sqrt{M_1M_2}/(c^2\sqrt{r_1r_2})$ scales as $r^{-1}$
and generates the Newtonian binding energy.  The spin-coupling terms
$A_1B_2$ and $A_2B_1$ describe how body~2's spin drags space through
body~1's mass field and vice versa---a genuinely two-body effect.  All these
arise from the QGD master metric; \emph{no GR input is used}.

%-------------------------------------------------------------
\subsection{Reduction to the three-body metric (pure QGD)}

For $N=3$, define $A_3=\sigma_t^{(3)}$, $B_3=\sigma_\phi^{(3)}$ and expand:

\begin{align}
  g_{tt} &= -\!\Biggl[1
    - \underbrace{A_1^2 + A_2^2 + A_3^2}_{\text{3 self-energy terms}}
    - \underbrace{2(A_1A_2 + A_1A_3 + A_2A_3)}_{\text{3 mass cross-terms}}
  \Biggr],
  \label{eq:gtt_3body}\\[6pt]
  \frac{g_{t\phi}}{-r\sin\theta}
  &= \underbrace{A_1B_1 + A_2B_2 + A_3B_3}_{\text{3 self frame-drag}}
  + \underbrace{A_1B_2 + A_2B_1 + A_1B_3 + A_3B_1 + A_2B_3 + A_3B_2}_{\text{6 cross frame-drag}},
  \label{eq:gtphi_3body}\\[6pt]
  g_{\phi\phi}
  &= r^2\sin^2\theta\!\left[1
    + \underbrace{B_1^2+B_2^2+B_3^2}_{\text{3 spin-sq.\ terms}}
    + \underbrace{2(B_1B_2+B_1B_3+B_2B_3)}_{\text{3 spin-spin couplings}}
  \right].
  \label{eq:gphiphi_3body}
\end{align}

The three-body metric contains 6+9+6 = 21 terms in total.  All arise
algebraically from $\sigma$-field superposition; no approximation is made.

\begin{table}[h]
  \centering
  \caption{Cross-term counting: the $N$-body metric is an exact algebraic object}
  \label{tab:nbody_terms}
  \begin{tabular}{@{}ccccc@{}}
    \toprule
    $N$ & $g_{tt}$ terms & $g_{t\phi}$ terms & $g_{\phi\phi}$ terms & Total \\
    \midrule
    1 & 1 & 1 & 1 & 3 \\
    2 & 3 & 4 & 3 & 10 \\
    3 & 6 & 9 & 6 & 21 \\
    5 & 15 & 25 & 15 & 55 \\
    10 & 55 & 100 & 55 & 210 \\
    $N$ & $N(N+1)/2$ & $N^2$ & $N(N+1)/2$ & $N^2+N(N+1)$ \\
    \bottomrule
  \end{tabular}
\end{table}

\begin{corollary}{Computational efficiency}{complexity}
  Evaluating the $N$-body metric requires $O(N)$ field evaluations plus two
  summations and two squarings per field point.  This is in sharp contrast
  with numerical GR, which requires $O(N_{\mathrm{grid}}^3\times N_{\mathrm{steps}})$
  operations with $N_{\mathrm{grid}}\sim10^9$.  The QGD superposition principle
  makes $N$-body astrophysical simulations algebraically tractable.
\end{corollary}

\medskip
\noindent\textit{Remark on the radial metric component.}  In the isotropic
form of the master metric (which is derived directly from
Eq.~\eqref{eq:master}), $g_{rr}=1$ for each isolated source.  The relation
$g_{rr}=-1/g_{tt}$ that appears in two-body expressions corresponds to
working in curvature coordinates and is an additional coordinate choice, not
a consequence of the master metric.  For genuine $N$-body work, the isotropic
form is the natural choice.

%=============================================================
\section{Summary: GR vs QGD}
\label{sec:comparison}
%=============================================================

\begin{table}[h]
  \centering
  \caption{Paradigm comparison}
  \label{tab:comparison}
  \renewcommand{\arraystretch}{1.2}
  \begin{tabular}{@{}lll@{}}
    \toprule
    \textbf{Aspect} & \textbf{General Relativity} & \textbf{QGD} \\
    \midrule
    Fundamental variable & $g_{\mu\nu}$ (10 components) & $\sigma_\mu$ (4 components) \\
    Metric status & Fundamental & Derived output \\
    Field equations & 10 coupled nonlinear PDEs & 4 linear + algebra \\
    Superposition & Impossible at metric level & Exact at $\sigma$-level \\
    Singularities & Generic, unavoidable & Resolved at $\lambda_C$ \\
    Gravitational energy & Pseudotensor & True tensor $\tfrac{1}{2}(\partial\sigma)^2$ \\
    Einstein equations & Postulated & Derived (equilibrium $\nabla^2\sigma = 0$) \\
    Exactness of composite metric & N/A & Theorem~\ref{thm:einstein_recovery} \\
    Computational cost & Exponential (numerical) & Polynomial (algebraic) \\
    \bottomrule
  \end{tabular}
\end{table}

\end{document}
